% !TEX root = ../arxiv.tex
\ifarxiv
\section*{Contribution Statement}
All authors contributed to the high-level idea and writing of the paper. MR contributed to the code base for running attribute-based few-shot learning experiments, discovered that unsupervised learning plus finetuning is beneficial, performed experiments on Celeb-A, and created most of the figures and graphics. ET helped with figure creation, implemented the flexible few-shot version of Zappos-50K and ran the experiments on that dataset. KCW contributed to the FFSL task definition, implemented the ImageNet-with-Attributes FFSL benchmark, and the associated code for using the off-the-shelf models. JL designed and implemented early experiments in the FFSL setting, provided the formal description of FFSL, and analyzed the linear toy problem presented in Appendix E. JS contributed to the analysis of early FFSL experiments. XP and AT contributed ideas about the underlying question and its possible solutions, and helped interpret results. RZ contributed many ideas behind the underlying question studied here and the
problem formulation, and led the team's brainstorming about how to test the hypotheses, the datasets and benchmarks, and modeling approaches and visualizations.

\section*{Acknowledgments}
We would like to thank Claudio Michaelis for several helpful discussions about the problem formulation, Alireza Makhzani for related generative modeling ideas, and Mike Mozer for discussions about contextual similarity. Resources used in preparing this research were provided, in part, by the Province of Ontario, the
Government of Canada through CIFAR, and companies sponsoring the Vector Institute
(\url{www.vectorinstitute.ai/\#partners}). This project is supported by NSERC and the Intelligence
Advanced Research Projects Activity (IARPA) via Department of Interior/Interior Business Center
(DoI/IBC) contract number D16PC00003. The U.S. Government is authorized to reproduce and distribute
reprints for Governmental purposes notwithstanding any copyright annotation thereon. Disclaimer: The
views and conclusions contained herein are those of the authors and should not be interpreted as
necessarily representing the official policies or endorsements, either expressed or implied, of
IARPA, DoI/IBC, or the U.S. Government.
\fi